Kelompok 4_Praktikum_Pekan 9

### 2024-04-23 Project/Kelompok 4_Praktikum_Pekan 9.Rmd
Update

---
title: "Kelompok 4_Praktikum_Pekan 9"
author: "Angga Fathan Rofiqy"
date: "2024-04-21"
output: html_document
---

@@

> <mark style="background-color: #6ec1c1">**Rpubs :**</mark><https://rpubs.com/ZenR_Prog/MSR-Prak-08>

@@

par(mfrow = c(1, 2))
hist(n100)
hist(n500)
```

@@

```{r fig.height=3.5, fig.width=7.5, dpi=300}
set.seed(50)
sample.250 <- rnorm(250, mean = 60, sd = 4)
hist(sample.250)
```

>>>>

---
title: "Kelompok 4_Praktikum_Pekan 9"
author: "Angga Fathan Rofiqy"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: show
    toc_depth: 3
    number_sections: false
    toc_float:
      collapsed: true
      smooth_scroll: true
    fig_caption: true
pkgdown:
  as_is: true
---

@@

**Kelompok 4 Pararel 2**

| Nama                 | NIM           |
|----------------------|---------------|
| Angga Fathan Rofiqy  | `G1401211006` |
| Gladys Adya Zafira   | `G1401211014` |
| Kheni Hikmah Lestari | `G1401211029` |

@@

par(mfrow = c(1, 2))
hist(n100, col = "#6ec1c1")
hist(n500, col = "#357a87")
```

@@

```{r fig.height=3.5, fig.width=7.5, dpi=300}
set.seed(50)
sample.250 <- rnorm(250, mean = 60, sd = 4)
hist(sample.250, col = "#e9865b")
```
